\section{State of the art}
% Describe what others have done to solve the same industrial challenge. Provide references.

Van Damme et al.~\cite{VanDammeSam2024Iolo} demonstrated that latency critically affects collaborative VR quality of experience (QoE): $\leq 75$ms RTT provides good collaboration, while $>300$ms causes severe degradation ($p<0.001$). Co-located systems using WiFi 6E can achieve $<30$ms latency, but Quest 3 validation is needed.

Reimer et al.~\cite{ReimerDennis2021CfSV} compared calibration methods for Quest devices, finding hand tracking achieved best accuracy ($\sim$10mm error) without additional hardware. This establishes the safety-critical threshold for collision prevention. However, only 2 Quest 1 devices were tested; Quest 3 validation with three headsets over 30--60 minute sessions remains unaddressed.

Chen et al.~\cite{ChenLei2024Eoep} evaluated World-in-Miniature (WIM) interfaces (n=36), demonstrating significant improvements over 2D maps ($p<0.05$) for collaborative tasks. WIM effectiveness increases with task complexity, but 3-user co-located configurations are unexplored.

Weiss et al.~\cite{WeissYannick2025ItEo} showed visual consistency across headsets is essential—asymmetric representations significantly degrade collaborative performance (n=30). Co-located systems require symmetric views and $<10$mm calibration to maintain consistency.

Schild et al.~\cite{SchildJonas2018E—Ev} evaluated paramedic VR training (n=24), revealing 66.7\% rated tethered systems with poor usability (SUS $<70$) due to cables. Strong correlations emerged between usability and presence ($r=0.73$, $p<0.001$ for experienced realism). Wireless headsets should dramatically improve these metrics.

\subsection{Evidence-Based Requirements}

\begin{table}[h]
\centering
\caption{Evidence-Based Technical Requirements}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Requirement} & \textbf{Target} & \textbf{Source} \\
\hline
Calibration & $<10$mm & \cite{ReimerDennis2021CfSV} \\
Latency & $\leq 75$ms & \cite{VanDammeSam2024Iolo} \\
Frame Rate & $\geq 90$ fps & \cite{SchildJonas2018E—Ev} \\
Spatial UI & WIM & \cite{ChenLei2024Eoep} \\
Usability & SUS $>70$ & \cite{SchildJonas2018E—Ev} \\
\hline
\end{tabular}
\end{table}